### 2023-06-01 paper/localpsf.tex
add figures created by Tucker to paper

\begin{figure}
	\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c c c c}
				noise    & \multicolumn{5}{c}{COND$(\bm{\preconditioner}^{-1} \bm{H})$ } \\ \cline{2-6}
				level    & REG     &	NONE  & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ \hline 
				$25\%$   & 1.68e+3 & 2.16e+3  & 1.37e+0   & 1.30e+0   & 1.21e+0    \\ 
				$11\%$   & 9.19e+3 & 9.08e+2  & 1.85e+0   & 1.49e+0   & 1.27e+0    \\   
				$5.0\%$  & 3.66e+4 & 4.67e+2  & 3.46e+0   & 2.62e+0   & 1.91e+0    \\ 
				$2.2\%$  & 1.41e+5 & 8.25e+2  & 1.16e+1   & 4.99e+0   & 3.20e+0    \\  
				$1.0\%$  & 6.06e+5 & 1.70e+3  & 3.44e+1   & 5.38e+1   & 7.06e+0    \\   
			\end{tabular}
			\endgroup
		\end{center}
	\caption{Condition number for $\bm{\preconditioner}^{-1} \bm{H}$ for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), no preconditioner (NONE) and regularization (REG). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for 
	the regularization value $\gamma$ as determined by the respective noise level and the Morozov discrepancy principle.}
	\label{fig:condition_number}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.25]{adv_ic_true_tmp.png}
		%		\caption{}
		%		\label{fig:newtoniter2}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.25]{velocity_tmp.png}
		%		\caption{}
		%		\label{fig:newtoniter1}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.25]{adv_final_condition_true_tmp.png}
		%		\caption{}
		%		\label{fig:newtoniter3}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.25]{adv_reconstruction_tmp.png}
		%		\caption{}
		%		\label{fig:newtoniter4}
	\end{subfigure}
	%\begin{subfigure}{0.05\textwidth}
	%	\includegraphics[scale=0.1]{mColorBar.png}
	%\end{subfigure}
	\caption{(a) true initial condition. (b) velocity field. (c) observed concentration at final time. (d) reconstruction of initial condition. black=0, white=1}
	\label{fig:adv_inversion1} 
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[scale=0.75]{adv_vary_kappa_tf_tmp.png}
	\end{center}
	\caption{Impulse responses for various diffusivities kappa and fixed simulation time Tf=0.5 (top) and simulation times with fixed kappa=1e-3 (bot). Colorbar is normalized independently for each subfigure}
	\label{fig:adv_vary_kappa_tf}
\end{figure}

>>>>

\begin{table}
	\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c c c c}
				noise    & \multicolumn{5}{c}{COND$(\bm{\preconditioner}^{-1} \bm{H})$ } \\ \cline{2-6}
				level    & REG     &	NONE  & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ \hline 
				$25\%$   & 1.68e+3 & 2.16e+3  & 1.37e+0   & 1.30e+0   & 1.21e+0    \\ 
				$11\%$   & 9.19e+3 & 9.08e+2  & 1.85e+0   & 1.49e+0   & 1.27e+0    \\   
				$5.0\%$  & 3.66e+4 & 4.67e+2  & 3.46e+0   & 2.62e+0   & 1.91e+0    \\ 
				$2.2\%$  & 1.41e+5 & 8.25e+2  & 1.16e+1   & 4.99e+0   & 3.20e+0    \\  
				$1.0\%$  & 6.06e+5 & 1.70e+3  & 3.44e+1   & 5.38e+1   & 7.06e+0    \\   
			\end{tabular}
			\endgroup
		\end{center}
	\caption{Condition number for $\bm{\preconditioner}^{-1} \bm{H}$ for our preconditioner with 1, 5, and 25 batches (PSF (1), PSF (5), and PSF(25), respectively), no preconditioner (NONE) and regularization (REG). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for 
	the regularization value $\gamma$ as determined by the respective noise level and the Morozov discrepancy principle.}
	\label{fig:condition_number}
\end{table}

@@

\begin{figure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.14]{true_initial_condition.png}
		%		\caption{}
		%		\label{fig:newtoniter2}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.14]{wind_velocity_colorscheme3.png}
		%		\caption{}
		%		\label{fig:newtoniter1}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.14]{noisy_observations_T1.0_K3.2e-4.png}
		%		\caption{}
		%		\label{fig:newtoniter3}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.14]{reconstructed_initial_condition_T1.0_K3.2e-4.png}
		%		\caption{}
		%		\label{fig:newtoniter4}
	\end{subfigure}
	%\begin{subfigure}{0.05\textwidth}
	%	\includegraphics[scale=0.1]{mColorBar.png}
	%\end{subfigure}
	\caption{(Left) True initial condition. (Middle left) Velocity field. Color indicates magnitude of velocity vector. (Middle right) Noisy observations of concentration at final time. (Right) Reconstructed initial condition.}
	\label{fig:adv_inversion1} 
\end{figure}

\begin{table}
	\begin{center}
		\begingroup
		\setlength{\tabcolsep}{8pt}
%		\renewcommand{\arraystretch}{1.25}
		\renewcommand{\arraystretch}{1.0}
		\begin{tabular}{c| c | c c c c c}
			& $\kappa$    & REG     &	NONE   & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ 
			\hline 
			& $1.0e{-4}$    & 584 & 317  & 311   & 151   & 56    \\ 
%			& $1.8e{-4}$    & 628 & 313  & 192   & 131   & 49    \\   
	$T=0.5$ & $3.2e{-4}$    & 685 & 311  & 233   & 140   & 44    \\ 
%			& $5.6e{-4}$    & 734 & 310  & 334   & 144   & 40    \\  
			& $1.0e{-3}$    & 702 & 324  & 122   & 71   & 33    \\ 
			\hline
			& $1.0e{-4}$    & 634 & 449  & 539   & 288   & 100    \\ 
%			& $1.8e{-4}$    & 665 & 449  & 493   & 212   & 84    \\   
	$T=1.0$ & $3.2e{-4}$    & 681 & 459  & 350   & 202   & 90    \\ 
%			& $5.6e{-4}$    & 619 & 482  & 262   & 197   & 70    \\  
			& $1.0e{-3}$    & 574 & 520  & 266   & 260   & 208    \\ 
			\hline
			& $1.0e{-4}$    & 609 & 591  & 548   & 520   & 165    \\ 
%			& $1.8e{-4}$    & 576 & 611  & 434   & 426   & 185    \\   
	$T=2.0$ & $3.2e{-4}$    & 524 & 645  & 318   & 379   & 170    \\ 
%			& $5.6e{-4}$    & 464 & 711  & 480   & 289   & 153    \\  
			& $1.0e{-3}$    & 349 & 786  & 381   & 262   & 158    \\ 
		\end{tabular}
		\endgroup
	\end{center}
	\caption{Number of preconditioned conjugate gradient iterations required to achieve relative error $10^{-6}$ for solving the Newton linear system in the advection-diffusion inverse problem. Iteration counts are shown for a variety of different diffusion parameters $\kappa$, simulation times $T$, and preconditioners.}
	\label{tab:adv_convergence}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{cccc}
		  & $T=0.5$ & $T=1.0$ & $T=2.0$ \\
		$\kappa=1.0e{-4}$  & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-4.png} \\
		$\kappa=3.2e{-4}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K3.2e-4.png} \\
		$\kappa=1.0e{-3}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-3.png}
	\end{tabular}
	\caption{Impulse responses for a variety of different diffusion parameters $\kappa$ and simulation times $T$.}
	\label{tbl:table_of_figures}
\end{table}

\begin{figure}
	\caption{Impulse responses for various diffusivities kappa and fixed simulation time Tf=0.5 (top) and simulation times with fixed kappa=1e-3 (bot).}
	\label{fig:adv_vary_kappa_tf}
\end{figure}
